\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}


\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\large\bfseries}
{}
{0em}
{}

\titlespacing\section{0pt}{0pt}{0pt}
\titlespacing\subsection{0pt}{0pt}{0pt}


\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries
\theauthor}

\end{center}
}

\begin{document}

\title{R\'esum\'e}
\author{Sounak Bhattacharya}

\maketitle

\begin{center}
{\Large sounak.bhattacharya@gmail.com}\\
\href{https://www.linkedin.com/in/sounak-bhattacharya-b67718139/}{LinkedIn}\\
\href{https://github.com/bsounak}{GitHub}\\
\href{https://stackoverflow.com/users/4233113/sounak}{stackoverflow}\\
+358 44 263 7571
\end{center}

\section{Summary}
\subsection{}
I am a software engineer with 7 years of experience in the field of Machine
Vision/Computer Vision and Industrial Robotics. I am also a passionate coder
who loves writing usable, maintainable and well-designed software. I like to
work in challenging roles. I am an excellent team player with great
communication skills. I also love to work independently and solve problems on
my own when the opportunity arises.
\subsection{}

\section{Technical Expertise}
\subsection{}
\begin{itemize}[label={}]
  \itemsep0em 
  \item\textbf{Programming Languages} Python, C, C++, Objective C, MATLAB
  \item\textbf{Domain Knowledge:} Imaging, Machine/Computer Vision, Augmented Reality,
    Virtual Reality, Signal Processing, Machine Learning.
  \item\textbf{Software Tools:} Vim, Microsoft Visual Studio Code, Pycharm,
    Git, Jenkins, LaTeX
  \item\textbf{Operating Systems:} macOS, Ubuntu, Debian, Windows
  \item\textbf{Project Management Tools:} Atlassian Jira
  \item\textbf{Expertise:} Image Processing, Machine/Computer Vision, Robotics and Test Automation, Cross Platform Software Development, Data Science.
  \item\textbf{Libraries:} OpenCV, Numpy, SciPy, Pandas, scikit-learn, Halcon
\end{itemize}

\subsection{}

\section{Work Experience}
\subsection{}
\textbf{OptoFidelity Oy. (Imaging Engineer),} October 2017 -
\begin{itemize}[label={}]
  \item \textbf{Automated Testing of AR/VR Head Mounted Displays}
    \begin{itemize}[label={--}]
      \item Worked on machine vision problems related to testing Head Mounted
        Displays.  This includes writing camera drivers, performing camera
        calibrations, designing camera alignment algorithms for Head Mounted
        Displays, designing and implementing algorithms for different analyses and
        implementing standard measurement methods e.g, IEC 63145-20-10
    \end{itemize}

  \item \textbf{Display Inspection}
    \begin{itemize}[label={--}]
    \item Worked on various projects related to software and imaging algorithms
      for display test automation.
    \item Worked for undisclosed client (Internal name: Sauna). This project
      involved porting and optimizing production ready image analysis algorithms,
      which was in MATLAB, to Objective-C. Delivered project on site.
    \end{itemize}

  \item \textbf{IQC Software Development}
    \begin{itemize}[label={--}]
      \item Worked for undisclosed client (Internal name: Sauna). This project
        involved developing an IQC (Internal Quality Control) tester for clients
        various different internal components.  Delivered project on site.
    \end{itemize}

\end{itemize}

\subsection{}
\textbf{Tampere University of Technology (Research Assistant),} September 2014 -
  October 2017
\begin{itemize}[label={}]
  \item \textbf{3D Point Clouds}
    \begin{itemize}[label={--}]
      \item Worked as a research assistant in the department of signal processing
        on projects which involved collaborations between Tampere University of
        Technology and Nokia Technologies.  The work mainly involved working with
        3D point clouds generated from Lidar data and feature extraction from these
        large scale 3D datasets.
    \end{itemize}
  \item \textbf{Machine Learning: Surface Classification}
    \begin{itemize}[label={--}]
      \item Worked on classification of glass and glass like surfaces. 
    \end{itemize}
\end{itemize}

\section{Education}
\subsection{}
\textbf{Tampere University of Technology (Master's degree),} 2013 - 
\begin{itemize}[label={--}]
  \itemsep0em 
  \item Major in Signal Processing (Thesis pending). Minor in Information
    Technology.
  \item GPA: 4.2/5
\end{itemize}

\subsection{}
\textbf{West Bengal University of Technology (Bachelor's degree),} 2008-2012
\begin{itemize}[label={--}]
  \itemsep0em 
  \item Major in Computer Science
  \item Cumulative GPA: 7.39/10
\end{itemize}


\section{Publications}
\subsection{}
\begin{itemize}[label={--}]
  \itemsep0em 
  \item Bhattacharya S., Fan L., Babahajiani P., Gabbouj M. (2016) Global Scale
    Integral Volumes. In: Computer Vision – ECCV 2016 Workshops. ECCV 2016.
\end{itemize}

\section{Patents}
\subsection{}
\begin{itemize}[label={--}]
  \itemsep0em 
  \item Method and apparatus for processing signal data - US20160232420A1
\end{itemize}

\section{Interests}
\subsection{}
Music, Cinema, Badminton, Reading, Running.
\subsection{}


\section{References}
\subsection{}
\begin{itemize}[label={}]
\itemsep0em 
  \item \textbf{Ranjeeth Shetty}
  \item Software Engineer Project Lead
  \item OptoFidelity Oy.
  \item \href{mailto:me@example.com}{ranjeeth.shetty@optofidelity.com}

  \item 

  \item \textbf{Joni Piililä}
  \item Chief Operating Officer (COO)
  \item OptoFidelity Oy.
  \item \href{mailto:me@example.com}{joni.piilila@optofidelity.com}
\end{itemize}

\subsection{}


\end{document}
